---
title: "2022/05/13"
author: "Runxin Lin (2392284)"
output:
  html_document:
    toc: yes
---

```{r}
set.seed(12345)
```

#### Assign random values to "df_Betas"
```{r}
N = 10
Share_Names <- paste0("Share_", 1:N)
Betas <- t(data.frame(beta = rnorm(N, mean = 1, sd = 0.2), row.names = Share_Names))
Betas
```

#### rank() function gives the respective rank of the numbers present in the vector
```{r}
beta_rank <- rank(Betas)
names(beta_rank) <- Share_Names
beta_rank
```

#### It is clearly that the rank function gives the rank of the values in a vector if the vector is sorted but in the same sequence as the original vector. Thus, rank according to scores does not work here.
```{r}
names(beta_rank)[beta_rank]
```

#### On the other side, the order function gives the position of the original value in the vector but in the sequence of the sorting in ascending order.
```{r}
beta_order <- order(Betas)
names(beta_order) <- Share_Names
beta_order
```

#### If you put these indices in this order, you will get the sorted vector.
```{r}
names(beta_order)[beta_order]
```

#### The reason why rank() function works in your example is because the order of it happens to be the same as the order() function.
```{r}
Betas <- t(data.frame(beta =c(0.1838,0.3096,0.6213,0.8275,0.7356,1.1754,1.1566,1.8672,1.4322,1.8778), row.names = Share_Names))

beta_rank <- rank(Betas)
names(beta_rank) <- Share_Names

beta_order <- order(Betas)
names(beta_order) <- Share_Names

beta_rank == beta_order
```






